Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
restructure related works

The emergence of new technology has in the past often required operating systems
to change. Traditionally, OS researchers and developers benchmark and test their
solutions in new environments to demonstrate their efficacy before using them in
real systems. However, researchers do not always have access to new technology
for practical reasons; for example, large memory systems are still too expensive
for most research budgets. This is not the first time that researchers have been
forced to study systems in environments they do not have access to. This section
examines past approaches to studying these systems and motivates the need for
our work.

@@

(TODO: where to put this paragraph?)
A study of recent changes to memory management in Linux has found that there
has been a lot of focus on improving the scalability of data structures used in
the Linux memory manager \cite{huang2016evolutionary}. Since systems with
persistent memory are expected to have large amounts of memory, there have been
efforts to reduce the overheads of \texttt{struct page}. This is because these
structures can consume several gigabytes of memory for systems with terabytes
of persistent memory \cite{corbet_persistent_progress}. These structures need
to be stored in volatile memory not only because they need to be accessed
quickly for performance reasons, but also to avoid wearing out of persistent
memory due to frequent writes to this data structure. Patches proposed to the
Linux kernel have proposed getting rid of the \texttt{struct page} altogether, but the
complexity associated with such radical changes have hindered their acceptance
by the community.

>>>>

The emergence of new technology has in the past often required operating systems
to change. A study of recent changes to memory management in Linux has found that there
has been a lot of focus on improving the scalability of data structures used in
the Linux memory manager \cite{huang2016evolutionary}. Since systems with
persistent memory are expected to have large amounts of memory, there have been
efforts to reduce the overheads of \texttt{struct page}. This is because these
structures can consume several gigabytes of memory for systems with terabytes
of persistent memory \cite{corbet_persistent_progress}. These structures need
to be stored in volatile memory not only because they need to be accessed
quickly for performance reasons, but also to avoid wearing out of persistent
memory due to frequent writes to this data structure. Patches proposed to the
Linux kernel have proposed getting rid of the \texttt{struct page} altogether.

Traditionally, OS researchers and developers would benchmark and test such
solutions in new environments to demonstrate their efficacy before using them in
real systems. However, researchers do not always have access to new technology
for practical reasons; for example, large memory systems are still too expensive
for most research budgets. This is not the first time that researchers have been
forced to study systems in environments they do not have access to. This section
examines past approaches to studying these systems and motivates the need for
our work.

@@
